### 2021-10-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@60079a1e76ef77faff90185f4192f4756f9e647b 🚀

\emph{title ideas}: Forecasting the spatio-temporal uncoupling of
bumblebee-flower interaction networks

@@

@@

\begin{itemize}
\tightlist
\item
  range shifts in latitude context
\item
  apply this to elevational gradients
\item
  dispersal capacity and range shifts
\end{itemize}

@@

The remote-sensing data consists of high-resolution LiDAR elevation data
at 1 meter spatial resolution {[}(NEON) (2021);{]}, and daily 1km
resolution precipitation and temperature from CHELSA (Karger \emph{et
al.} 2021).

@@

\leavevmode\hypertarget{ref-NationalEcologicalObservatoryNetworkNEON2021EleLid}{}%
(NEON), N.E.O.N. (2021). Elevation - LiDAR (DP3.30024.001):
RELEASE-2021.

>>>>

@@

Earth's ecosystems are subject to rapid change due to both climate and
land-use change (\textbf{cite?}). These sudden shifts in environment
alter both the spatial and temporal distribution of species.

Ecosystems are composed of interactions between species.

Species vary in spacem but also

@@

\begin{itemize}
\tightlist
\item
  range shifts in latitude context
\item
  apply this to elevation gradients
\item
  dispersal capacity and range shifts
\end{itemize}

@@

The remote-sensing data consists of 15-arcsecond elevation
data(\textbf{GMTED2020?}, cite), and daily 1km resolution precipitation
and temperature from CHELSA (Karger \emph{et al.} 2021).

@@
